CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability and GPUs

### 2019-03-22 gpus/paper.tex
some updates to summary

In this paper, we describe our approach to performance portability
with the \castro\ multiphysics simulation code.  We choose not to use
a framework like Kokkos but instead we implement the mechanism for
offloading compute kernels to GPUs inside of the AMReX adaptive mesh
refinement library itself.  Our goal is to have the same computational
kernels run efficiently on CPUs (including manycore processors) and
GPUs.  Early GPU results with a version of \castro\ were desribed in
\citet{astronum:2017}.  Here, we describe the work we needed to do to
enable this portability and show performance metrics for a reacting
flow problem in astrophysics.

@@

>>>>

In this paper, we describe our approach to performance portability
with the \castro\ multiphysics simulation code.  We choose not to use
a framework like Kokkos but instead we implement the mechanism for
offloading compute kernels to GPUs inside of the AMReX adaptive mesh
refinement library itself.  Our goal is to have the same computational
kernels run efficiently on CPUs (including manycore processors) and
GPUs.  Early GPU results with a version of \castro\ were described in
\citet{astronum:2017}.  Here, we describe the work we needed to do to
enable this portability and show performance metrics for a reacting
flow problem in astrophysics.

@@

The Nyx cosmological code branched from \castro\ some time ago, but
they share a lot of the same compute kernels, so it should porting the
GPU-based hydro solver to Nyx is straightforward (and already in
progress).
